%!TEX TS-program = lualatex
\documentclass[]{friggeri-cv}
\usepackage[none]{hyphenat}
\usepackage{fontspec}
\usepackage{fontawesome}

\begin{document}
\header{Alexandre }{Arpin}
       {Software Developer}
       {\faCloud ~alexandrearpin.com~ | \faHome ~Montreal, Qc~ | ~ \faPhone ~(514) 730-6126~ | ~\faEnvelopeAlt  ~arpin.alexandre@gmail.com}

\section{education}

\begin{entrylist}
  \entry
    {2011-2016}
    {B.Eng {\normalfont Software Engineering}}
    {École de technologie supérieure}
    {}
    {0cm}
  \entry
    {2008-2011}
    {DCS. {\normalfont Computer Science Technology}}
    {Collège Ahuntsic}
    {}
    {0cm}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {2016}
    {GSOFT, Montreal}
    {C\#, WPF, ASP.NET MVC, html5, sass, gulp}
    {\emph{Design, development and maintenance of Sharegate, a governance and migration tool for SharePoint environnements.}
    \vspace{0.1cm}
    \begin{itemize}
      \item Delivered quality features spanning the full development stack
      \item Maintained high quality standards through unit tests and documentation
      \item Developed and deployed high scalability applications using Microsoft Azure Services
    \end{itemize}}
    {0.3cm}
  \entry
    {2015}
    {Resulto, Montreal}
    {python, django, django-rest-framework, html5, sass, gulp}
    {\emph{Design, development and maintenance of LoyalAction, a solution for customer loyalty.}
    \vspace{0.1cm}
    \begin{itemize}
      \item Delivered quality features spanning the full development stack
      \item Integrated third-party applications and services seamlessly
      \item Maintained high quality standards through unit tests and documentation
      \item Researched and implemented a unique non-sequential number generation algorithm
      \item Published useful tools as PyPi packages for the open-source community
    \end{itemize}}
    {0.3cm}
  \entry
    {2013-2014}
    {Beehivr Technologies, Repentigny}
    {C\#, ASP.NET MVC, WebApi, html5, css3, Android, Obj-C, JavaFX}
    {\emph{Design, development and maintenance of Beehivr, a point of engagement platform for iOS and Android.}
    \vspace{0.1cm}
    \begin{itemize}
      \item Delivered a fully featured administration dashboard to manage hundreds of iOS devices
      \item Developed a RESTful Web Api for the Beehivr applications and providers
      \item Collaborated on the design and code reviews of the Beehivr iOS application
      \item Ported and adapted the Beehivr iOS application to Android
      \item Developed a standalone JavaFX application to manage event guest lists
    \end{itemize}}
    {0cm}
\end{entrylist}

\section{projects}

\begin{entrylist}
 \entry
    {2016}
    {Root {\normalfont root.plants.ninja}}
    {slack, python, django}
    {A Slack integration to improve your workplace by integrating plants into it. Root will help you choose plants that best fit your needs and notify you when they need to be taken care of.}
    {0.1cm}
 \entry
    {2015}
    {Magic the Gathering Card Identifier {\normalfont alexandrearpin.com/mtg-card-identifier}}
    {python, django}
    {A library and web application that identify Magic: the Gathering cards in pictures through image recognition (OpenCV and Tesseract).}
    {0.1cm}
  \entry
    {2015}
    {Magic the Gathering Font {\normalfont alexandrearpin.com/mtg-font}}
    {html5, css3}
    {An easy to use web font inspired by FontAwesome for all of the Magic: the Gathering symbols.}
    {0.1cm}
  \entry
    {2014}
    {Unfinished Asteroids libGDX {\normalfont alexandrearpin.com/unfinished-asteroids-libgdx}}
    {Android}
    {For learning purposes, you are asked to act as new developer joining an unfinished Asteroid game project. A storyline then guides you through fixing known bugs and implementing new features in this classic arcade game.}
    {0cm}
\end{entrylist}
\end{document}
